---
title: "writing Reports with R markdown"
author: "Kai Han"
date: "2022-10-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages}
library(tidyverse)
library(here)
library(knitr)
```

This report was prepared for the UN. it analyzes the relationship between a country's GDP, life expectancy, and co2 emisions. Our goal was to determine to what degree o country;s economic strength or weakness may be related to its public healthy status and impact on climate pollution. We hypothesize that both life expectancy and co2 emmisions will increase with a country's GDP

```{r data, include = FALSE}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
```
```{r gdp_lifeexp_1997}
ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp, color = continent,size = pop/1000000))+geom_point()+
  labs(x = "GDP per capita",
       y = "Life expectancy",
       title = "Do people in wealthy countries live longer?",
     size = "Population (in millions)",
     color = "Continent")
```

```{r summary_data}
n_countries <- gapminder_1997 %>%
  select(country) %>%
n_distinct()
min_gdp <- gapminder_1997 %>%
  summarize(min = round(min(gdpPercap)))
max_gdp <- gapminder_1997 %>%
  summarize(max = round(max(gdpPercap)))

```



The above plot shows the relationship between the GDP  per capita and life expectancy for a total of `r n_countries`.For the set of countries, economic wealth ranged from a minimum of $`r min_gdp` to a maximum of $`r max_gdp` per capita.


```
|Summary of Data|
|------|------|
|Number of Countries|`r n_countries`|
|Minimum GDP per capita|`r min_gdp`|
|Maximum GDP per capita|`r max_gdp`|

```

```{r tables}
gapminder_1997 %>%
  filter(continent == "Oceania") %>%
  kable()
```

##list
### unordered lists
- **R**
- *ggplot()*
- ***stringr***

###ordered lists
1. **R**
   - **R**
   - *ggplot()*
   - ***stringr***
1. *ggplot()*
1. ***stringr***package
1. [RMarkdown Reference](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf)
      